\documentclass[letterpaper,11pt]{article}
\pagestyle{empty}

\usepackage{latexsym}
\usepackage{resume2}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}

\definecolor{mygrey}{gray}{.85}

\textheight=9.0in
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{0.375in}
\addtolength{\textwidth}{0.5in}
\addtolength{\topmargin}{-.375in}
\addtolength{\textheight}{0.75in}

\newcommand{\resitem}[1]{\item #1 \vspace{-5pt}}
\newcommand{\resbreak}{\vspace{0.1in}}

\newcommand{\resheading}[1]{{\large \colorbox{mygrey}{\begin{minipage}{\textwidth}{\textbf{#1 \vphantom{p\^{E}}}}\end{minipage}}}}

\newcommand{\resheader}
{
  \center{\textbf{\Large Corbin Souffrant}}
  \begin{tabular*}{7in}{l@{\extracolsep{\fill}}lr}
  {\footnotesize \underline{Address}}  & & {\footnotesize \underline{Contact}}\\
  {\footnotesize 507 E Green St. Apt. B} & & {\footnotesize souffra2@illinois.edu}\\
  {\footnotesize Urbana, IL 61801} & & {\footnotesize 812-381-3984}\\
  \end{tabular*}
}

\newcommand{\resexperience}[4]
{
  \begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
    \textbf{#1} & \footnotesize{#2}
  \end{tabular*}
  \begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
    \textit{#3} & \footnotesize{#4}
  \end{tabular*}
  \vspace{-8pt}
}

\newcommand{\resskill}[2]
{
  \footnotesize{\textbf{#1}}: \footnotesize{#2}\\
}

\newcommand{\resrandom}[3]
{
  \begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
    \textbf{#1} & \footnotesize{#3}\\
  \end{tabular*}
  \begin{tabular*}{6.5in}{l}
    #2
  \end{tabular*}
}

\begin{document}
\resheader

\resheading{Objective}
\footnotesize{Seeking a full time position after May 2014
graduation. I am considering a Master's degree, in which case I'm
looking for an internship.  Willing to work in the areas of Computer
Security Research, Vulnerability Discovery, and Malware
Analysis.}

\resheading{Education}
\begin{itemize}
\item %University of Illinois at Urbana-Champaign
  \begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
    \textbf{University of Illinois at Urbana-Champaign} &
    \footnotesize{Expected Graduation: May 2014}\\
  \end{tabular*}
  \begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
    \small{\textit{Bachelor of Science in Computer Science}} & \footnotesize{\textbf{GPA: 3.28/4.00}}
  \end{tabular*}
  \footnotesize{Relevant Courses: Computer Security, Computer Security
  Lab, Malware Analysis Lab, Undergraduate Research Lab, Applied
  Cryptography, Social Visualization, Security Reading Group, Network
  Security, Digital Forensics Lab}
\end{itemize}

\resheading{Experience}
\begin{itemize}
\item
  \resexperience{University of Illinois}{Urbana, IL}{Researcher}{Fall 2013}
  {\footnotesize
    \begin{itemize}
      \resitem{ Worked with both Professor Darko Marinov
                       and Professor Matthew Caesar on a new project
                       that aimed to detect incompatibilities between
                       code sources.  Involves analyzing previous
                       literature in the field and coming up with a
                       model to support our project.}
    \end{itemize}
  }
\item
  \resexperience{University of Illinois}{Urbana, IL}{Engineering
    Learning Assistant}{Fall 2013}
  {\footnotesize
    \begin{itemize}
      \resitem{ Helped encourage freshmen in Computer
                       Science to get the most out of their college
                       education.  Designed and presented lectures as
                       well as acting as a mentor for the students.}
    \end{itemize}
  }
\item
  \resexperience{Raytheon SIGOVS}{Annapolis Junction,
    MD}{Vulnerability Research and Development Intern}{Summer 2013}
  {\footnotesize
    \begin{itemize}
      \resitem{ Vulnerability Discovery using a variety of
                      methods.  Developed a smart fuzzer and setup a
                      testing framework.  Found bugs via source code
                      auditing.}
      \resitem{Worked with browser security
                      and applications on both x86 and ARM architectures.}
    \end{itemize}
  }
\item
  \resexperience{University of Illinois}{Urbana, IL}{Researcher}{Spring 2012 - Fall 2012}
  {\footnotesize
    \begin{itemize}
      \resitem{ Worked with Professor Sam King to design
                     and implement an application framework for
                     general purpose robots.  This involved developing
                     an API to communicate with the robot via a web
                     and android application.  Also wrote applications
                     in python and C++.}
      \resitem{ Presented a poster for
                     the research at a research symposium in Siebel in
                     Spring 2012.}
    \end{itemize}
  }
\end{itemize}

\resheading{Skills}
\begin{itemize}
\item
  \resskill{Static And Dynamic Analysis}{IDAPro, OllyDBG, GDB, Wireshark}
  \resskill{Vulnerability Discovery}{Fuzzer Development, Source Code
    Auditing, Testing Framework Design}
  \resskill{Malware Analysis}{Unpacking Techniques, Anti-debugging and
  Anti-reversing removal}
\item
  \resskill{Languages}{C, C++, Python, Java, x86, MIPS, OCaml}
  \resskill{Libraries}{openCV, ROS (Robot Operating System), Android}
  \resskill{Misc.}{svn, git, Emacs, Eclipse, Windows, Linux (Ubuntu, Arch)}
\end{itemize}

\resheading{Projects}
\begin{itemize}
\item
  \resexperience{Automated Malware Analysis}{Class Project}{}{Spring 2013}
  {\footnotesize
    \begin{itemize}
      \resitem{Set up a Virtual Machine that accepted binaries from a web
  interface.  I then used YARA and CuckooSandbox to process the binary
  and store the results in a database.  I worked with 3 other
  students for a semester project in the Security Lab course.}
    \end{itemize}
  }
\item
  \resexperience{Boston Bombing Spam/Malware Prevention}{Freelance}{}{Spring 2013}
  {\footnotesize
    \begin{itemize}
      \resitem{ Worked with John Bambenek to analyze a stream of spam related
  to the Boston bombing, analyzed domain registrations, basic malware
  reversing.}
      \resitem{Thanked on isc.sans.org (SANS Internet Storm Center) and featured on WAND local news.}
    \end{itemize}
  }
\item
  \resexperience{Quality Evaluation of Obfuscation}{Class Project}{}{Spring 2013}
  {\footnotesize
    \begin{itemize}
      \resitem{Attempted to develop a metric to allow for the development of
  a framework for analyzing the relative strength of an obfuscation
  routine.  I worked with one other student for a semester project in
  the Network Security course.}
      \resitem{Presented a poster at Siebel Center in Spring 2013.}
    \end{itemize}
  }
\item
  \resexperience{Malware Clustering Script}{Class Project}{}{Fall 2012}
  {\footnotesize
    \begin{itemize}
      \resitem{ Developed a simple malware cluster script written in python using the
  k-means algorithm.  This involved acquiring XML outputs from
  CWSandbox and modeling a feature-set from the results.  I wrote this
  as a final project for a statistics course.}
    \end{itemize}
  }
\item
  \resexperience{Security CTF Team Presenter}{ACM}{}{Fall 2012}
  {\footnotesize
    \begin{itemize}
      \resitem{ Designed and presented a series of lectures on skills required to
  participate in a Security CTF competition.}
    \end{itemize}
  }
\item
  \resexperience{Android Telemetry for a Vehicle}{EcoIllini}{}{Fall 2012 -
    Spring 2013}
  {\footnotesize
    \begin{itemize}
      \resitem{Developed an android application that communicated with an
  Arduino device connected to a car engine.  This provided real-time
  feedback on car speed, distance traveled, and time elapsed for the
  Ecoillini Shell Marathon Car.}
    \end{itemize}
  }
\end{itemize}

\resheading{Activities}
\begin{itemize}
\item
  \resskill{CSAW Security CTF 2012}{Placed 18th for qualifying teams
    with the ACM Security CTF Team.}
\item
  \resskill{Ebay Hackathon 2013}{Best Use of API for visualization of
    product sales.  I developed this with 3 team members.}
\item
  \resskill{IEEE Hackathon 2012}{Using OpenCV and an OCR script,
    developed an application that would read in a video feed from a
    webcam and record the ID number from a Student ID.}
\item
  \resskill{ACM Special Interest Group For Security}{Member since
    Spring 2012, Chair since Fall 2012.}
\item
  \resskill{Undergraduate Computer Science Research Symposium
    2012}{Presented a poster on my research with Sam King.}
\item
  \resskill{Illinois Technology Association Fall
    Challenge}{Participated in the finals of this software development
    competition.}
\end{itemize}

\end{document}